---
title: "Untitled"
author: "Maria C. Codlin"
date: "10/24/2017"
output: html_document
---
```{r}
install.packages("vrmlgen")
install.packages("geomorph")
install.packages("Morpho")
install.packages("abind")
```

```{r}
library(vrmlgen)
library(geomorph)
library(Morpho)
library(abind)
```

Import ply in ASCII format or use Morpho to import binary ply. 
```{r}
A1<-read.ply("A1.ply")#using Geomorph
```
```{r}
A2<-read.ply("A2.ply")
```
```{r}
T1<-file2mesh("T1.ply")#using Morpho
```

Use digit.fixed to selected fixed landmarks on the specimen, this will save a nts landmark file to the directory. You will use the console to confirm each point using y/n. Double right click to select the landmark. 
```{r}
A1_fix<-digit.fixed(A1, 10)#number of fixed landmarks to create
```
```{r}
A2_fix<- digit.fixed(A2, 10)#number of fixed landmarks to create
```

You can also read in landmark data from another software. Here we will read in the nts file from A1. 

```{r}
A1_fix2<-readland.nts("A1.nts")
```
```{r}
A2_fix<-readland.nts("A2.nts")
```
Read the nts files in to create a 3D array. 
```{r}
filelist<-(c("A1.nts", "A2.nts"))
filelist
a1_a2<-readmulti.nts(filelist)
```

Or bind the landmark files together into a 3d array for use in Geomorph using abind package. 
```{r}
dim(A1_fix)
A1_A2_fix<-abind(A1_fix, A2_fix, along=3)
dim(A1_A2_fix)
```
We can now view all the landmarks together, these are unaligned.
```{r}
plotAllSpecimens(a1_a2)
str(a1_a2)
```
We use the gpagen function to align the points
```{r}
GPA<-gpagen(a1_a2)
```
```{r}
str(GPA)
```

```{r}
plot3d(A1_fix2)
```

```{r}
plot(GPA)
```

I'm still not sure what the different shapes are right now. 




```{r}
plotspec(A1, A1_fix)
```

```{r}
str(A2_fix)
```

Create a surface with fixed and auto spaced landmark points (semi-something look up). 
```{r}
digitsurface(A1, , ptsize=1)
```

```{r}
vrml.open(file = "c60.wrl", html.embed = "example1.html", scale = 5)
data("c60coords")
points3d(c60coords, col = "black", scale = 5, hyperlinks = rep("http://wikipedia.org/wiki/Carbon", 60))
for(j in 1:(nrow(c60coords) - 1))
{
for(k in (j + 1):nrow(c60coords))
{
 if(sqrt(sum((c60coords[j, ] - c60coords[k, ])^2)) < 0.66) lines3d(c60coords[c(j, k), ], col = "gray", lwd = 3)
}
}
vrml.close()
browseURL(paste("file://", file.path(getwd(), "example1.html"), sep = ""))
```

install.packages("geomorph")
install.packages("rgl")
install.packages("ape", dependencies = TRUE)

```{r}
d<-read.ply("bun_zipper.ply")


```
```{r}
A2<-read.ply("A2.ply")
```

```{r}
plot3d(A1)
```
```{r}
A1_landmark<-digit.fixed(A1, 10, ptsize = 1)
```


```{r}
b_temp<- buildtemplate(A1, 10, surface.sliders = 100)
```

```{r}
A2<-read.ply("A2.ply")
```

```{r}
b_temp2<- buildtemplate(A2, 10, A1_landmark, surface.sliders = 100)
```
```{r}
fixed<-digit.fixed(A1, 10, center = FALSE)
```

```{r}
fixed<-(readland.nts("A1.nts"))
fixed
```
```{r}
A1_landmark
```


```{r}
A1_dsurf<-digitsurface(A1, "A1.nts")
```

```{r}
A1_array<- arrayspecs(fixed, 10, 3)
```

```{r}
digitsurface(A1, fixed=b_temp, ptsize = 1)
```
```{r}
str(b_temp)
```


```{r}
plotAllSpecimens("A1.nts")
```
```{r}
array_land<- arrayspecs("A1.nts", 10, k=3)
```

```{r}
d_surf<- digitsurface(A1, 4, ptsize = 1)
```


```{r}
T1<-file2mesh("T1.ply")
T12<-file2mesh("T1.ply")
A1<-file2mesh("A1.ply")
```


```{r}
summary(T1)
str(T1)
```
```{r}
head(d$vb)
```
```{r}

```

```{r}
plotAllSpecimens(d)
```

```{r}
buildtemplate(d, fixed=20)

```

```{r}
mesh2ply(d, "T1.2")
```

```{r}
plotspec(T1)
```
```{r}
digit.fixed(T12, 10)
```
```{r}
plot3d(T1)
```
```{r}
plot3d(A1_fix2)
```



